\documentclass{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{minted}
\usepackage{color}
\usepackage[english]{babel}

%
% Basic Document Settings
%

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\lhead{\hmwkAuthorName}
\chead{\hmwkClass\ (\hmwkClassInstructor): \hmwkTitle}
\rhead{\firstxmark}
\lfoot{\lastxmark}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}
\setlength{\parskip}{1em}

%
% Minted Settings
%

\setminted{frame=lines}
\setminted{linenos}
\setminted{autogobble}

%
% Create Problem Sections
%

\newcommand{\enterProblemHeader}[1]{
    \nobreak\extramarks{}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
    \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
}

\newcommand{\exitProblemHeader}[1]{
    \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
    \stepcounter{#1}
    \nobreak\extramarks{Problem \arabic{#1}}{}\nobreak{}
}

\setcounter{secnumdepth}{0}
\newcounter{partCounter}
\newcounter{homeworkProblemCounter}
\setcounter{homeworkProblemCounter}{1}
\nobreak\extramarks{Problem \arabic{homeworkProblemCounter}}{}\nobreak{}

%
% Homework Problem Environment
%
% This environment takes an optional argument. When given, it will adjust the
% problem counter. This is useful for when the problems given for your
% assignment aren't sequential. See the last 3 problems of this template for an
% example.
%
\newenvironment{homeworkProblem}[1][-1]{
    \ifnum#1>0
        \setcounter{homeworkProblemCounter}{#1}
    \fi
    \section{Problem \arabic{homeworkProblemCounter}}
    \setcounter{partCounter}{1}
    \enterProblemHeader{homeworkProblemCounter}
}{
    \exitProblemHeader{homeworkProblemCounter}
}

%
% Homework Details
%   - Title
%   - Due date
%   - Class
%   - Section/Time
%   - Instructor
%   - Author
%

\newcommand{\hmwkTitle}{Assignment\ \#2}
\newcommand{\hmwkDueDate}{February 28, 2019}
\newcommand{\hmwkClass}{CSE 6431}
\newcommand{\hmwkClassInstructor}{Professor Qin}
\newcommand{\hmwkAuthorName}{\textbf{Jeremy Grifski}}

%
% Title Page
%

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \normalsize\vspace{0.1in}\small{Due\ on\ \hmwkDueDate\ at 11:10am}\\
    \vspace{0.1in}\large{\textit{\hmwkClassInstructor}}
    \vspace{3in}
}

\author{\hmwkAuthorName}
\date{}

\renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}

%
% Various Helper Commands
%


% For derivatives
\newcommand{\deriv}[1]{\frac{\mathrm{d}}{\mathrm{d}x} (#1)}

% For partial derivatives
\newcommand{\pderiv}[2]{\frac{\partial}{\partial #1} (#2)}

% Integral dx
\newcommand{\dx}{\mathrm{d}x}

% Alias for the Solution section header
\newcommand{\solution}{\textbf{\large Solution}}

% Probability commands: Expectation, Variance, Covariance, Bias
\newcommand{\E}{\mathrm{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Bias}{\mathrm{Bias}}

\begin{document}

\maketitle

\pagebreak

\begin{homeworkProblem}

    \textbf{
        Lamport’s algorithm requires messages to be delivered in FIFO
        order between every pair of sites. Does Ricart-Agrawala’s algorithm
        require the same assumption to work? Explain your answer.
    }

    No! Since each process requires a REPLY from all other processes to begin
    executing their critical section AND the process with the lowest timestamp
    gets priority, there's no opportunity for multiple processes to hit
    their critical section at the same time even without the FIFO assumption.

    This differs from Lamport's algorithm because replies are combined with
    releases. In Lamport's algorithm, replies grant access to the critical
    section based on each process's local queue. If the communication channels
    are not FIFE, it's possible that the queues are not the same for all
    processes which means multiple processes can enter their critical section
    simultaneously. This is not a problem with the Ricart-Agrawala solution.

\end{homeworkProblem}

\pagebreak

\begin{homeworkProblem}

    \textbf{
        Show that in Lamport’s distributed mutual exclusion algorithm, the
        critical section is accessed according to the increasing order
        of timestamps. Then, show that the same property holds true in
        Ricart-Agrawal’s distributed mutual exclusion algorithm. Does the same
        hold true in Maekawa’s algorithm?
    }

    In Lamport's algorithm, the critical section is accessed according to the
    increasing order of timestamps due to the way request queues are handled.
    Every time a process receives a request, the request is placed onto that
    process's request queue in order of timestamp. These queues are synchronized
    between every processes, so all processes are aware of the order. At any
    given time, only the process with the smallest timestamp in the request
    queue can access its critical section.

    In Ricart-Agrawala's algorithm, the critical section is accessed according
    to the increasing order of timestamps due to the way replies are managed.
    Processes only send replies under two conditions:

    \begin{enumerate}
      \item They're not making a request
      \item They're making a request, but their timestamp is greater than an
      incoming request
    \end{enumerate}

    The second condition guarantees that processes access their critical section
    in increasing order of timestamps.

    Finally, the premise that the critical section is accessed according to the
    increasing order of timestamps does not hold for Maekawa's algorithm. It's
    precisely this fact which makes Maekawa's algorithm deadlock prone. Without
    using priority based on timestamps, the algorithm may generate a cycle between
    request sites which results in a deadlock.

\end{homeworkProblem}

\pagebreak

\begin{homeworkProblem}

    \textbf{
        If two logs are equivalent, are their serialization graphs identical? If
        yes, show your proof. Otherwise, give me a counter-example.
    }

    If a serialization graph has more than one topological sort, it's
    possible to construct multiple equivalent logs from that graph. In other
    words, two equivalent logs very well could have the same serialization
    graph. Whether or not they're guaranteed to have the same serialization
    graph is a tougher question to answer. To the best of my ability, I'm going
    to argue yes!

    Given a log, L1, there is only one serialization graph, G1, the can be
    constructed, assuming L1 is serializable (containing no cycles). In order
    for two logs, L1 and L2, to construct two different serialization graphs, G1
    and G2, but still be equivalent, their serialization graphs would have to
    have overlapping topological sorting sets, T1 and T2. In other words, the
    intersection of T1 and T2 would yield L1 and L2, but G1 and G2 wouldn't be
    equivalent. Is this possible?

    Unfortunately, it is not possible. In order to construct two graphs
    that share a topological sort but are different, we'd have to have two logs
    that are not equivalent which violates our assumption. In other words, we'd
    have to construct two logs that have different operations in them such as
    an extra write to incorporate an additional edge in the graph. The additional
    edge could allow for overlapping sorts, but the original logs would no
    longer be equivalent.

\end{homeworkProblem}

\pagebreak

\begin{homeworkProblem}

    \textbf{
        Consider a database system in which a set of transactions are executed.
        There are two requirements for correct execution of the transactions.
        First, the log of execution of operations in these transactions must be
        serializable. Second, the equivalent serial execution must follow a
        given partial order among the transactions. Describe a concise approach
        for verifying that the above two conditions are met by a log.
    }

    To verify that a log of execution is serializable, we must constuct a
    serialization graph using the condition that edge Ti → Tj then for some x
    either ri[x] < wj[x] or wi[x] < rj[x] or wi[x] < wj[x].

    From there, we need check that the graph has no cycles. To do so, we can use
    a depth first traversal to check if there are any back edges in the graph.

    The partial order is then generated from a topological sort. Topological
    sorts are not unique, so as long as the log interleaves the transactions
    in a way to preserve the partial order of one of the potential topological
    sorts it should be fine.

\end{homeworkProblem}

\pagebreak

\begin{homeworkProblem}

    \textbf{
        Assume a system has P processes and R identical units of a reusable
        resource. If each process can claim at most N units of a resource, show
        that the system will be deadlock free if and only if R >= P(N-1) + 1.
    }

    In English, there must be at least N number of units of a resource
    minus one used by P processes plus one to avoid a deadlock. After all, that
    makes sense. If each process can use at most N units of a resource, we'd
    need to have roughly that many resources times the number of processes
    available, so no processes are ever waiting. Or, more formally:

    \begin{enumerate}
      \item Let P be the number of processes a system has
      \item Let R be the number of identical units of a reusable resource
      \item Let N be the number of units of a resource that can be claimed by a
      process
      \item If a process needs at most N units of a resource to begin working,
      then at any given time we would need to satisfy that condition for at least
      one process. In other words, R has to be at least N. (base case)
      \item To avoid deadlocks, however, we would need to assume that all
      processes had consumed all remaining resources and needed just one unit
      of a resource to move on. In other words, one process has N resources and
      the remaining processes, (P-1), would have (N-1) resources.
      \item Put into an equation, we could say: R >= N + (P-1)(N-1).
      \item Distribute: R >= N + PN - P - N + 1
      \item Remove N: R >= PN - P + 1
      \item Factor P: R >= P(N-1) + 1
    \end{enumerate}

    In the end, we end up with the expected equation.

\end{homeworkProblem}

\pagebreak

\begin{homeworkProblem}

    \textbf{
        Consider a system consisting of m resources of the same type, being
        shared by n processes. Resources can be requested or released by
        processes only one at a time. Show that the system is deadlock free if
        the following two conditions hold:
        1) the maximum need of each process is between 1 and m resources, and
        2) the sum of all maximum needs is less than m + n.
    }

    Clearly, the first condition needs to be met because a process can't
    proceed if there were never enough resources to begin with.

    As for the second condition, the explanation is a bit more nuanced. The
    condition is that the sum of all maximum needs must be less than the
    sum of the number of process and the number of resources. As an example,
    if a process needs m resources, then there can only be 1 process as
    m + n > m.

    To prove the second condition, let's assume a system can have m + n
    resource needs. As an example, let's use a system that has 5 processes
    (n = 5) and 10 resources (m = 10). Then, m + n = 15. As a result, each process
    needs 3 resources such that the sum of all maximum needs is 15. Since there
    are only 10 resources, it's possible that all 5 processes accumulate those
    10 resources without any of them being able to process any work. In other
    words, a deadlock is possible.

    In the previous example, all we'd have to do is reduce one of the process's
    maximum need to 2, so the sum of all needs would be 14. Then, even if all
    processes were one away from being able to run, there would still be a
    resource left over for any of them to execute. 

\end{homeworkProblem}

\end{document}
